{\it E}nKCF: Ensemble of Kernelized Correlation Filters for Object Tracking in High Speed, 300Hz

### 2017-04-17 draft.tex
Cleaned up the list of the tracking methods to compare.

\begin{itemize}
\item Introduction: Should talk about, at least, motivation of this
  work, brief review of the literature, and contribution
\item Method: Detail the method w.r.t. a diagram of system
  architecture or pseudo code
\begin{itemize}
\item Kernelized Correlation Filter
\item A variant of KCF: Multiple KCF w/ PF ({\it E}nKCF, ${\it E}nKCF_{+RD}$
\item Re-detection for re-initialization: Modules for reliably
  detecting target-lost, for extensively searching the lost target,
  and for picking up the same target with a help from an appearance
  model or other models.
\begin{itemize}
\item To filter out unlikely box proposals,
\begin{itemize}
\item Use a prior information about box, our outputs, dimensions
  (e.g., a combination of width and height, aspect ratio, etc.)
\item Use the information about the trajectory of the target before we
  lose the target.
\end{itemize}
\item MTH: revisited
\item To make a box tighter, generate our own box proposals based on
  the locations of top $k$ box proposals from object proposal methods,
  e.g., Edge Box.
\end{itemize}
\end{itemize}
\item Experiment: Detail the data, and experimental setup; results and findings
\item {\it E}nKCF, Naive{\it E}nKCF, ${\it E}nKCF_{+RD}$, LCT, DSST,
  vanilla-KCF w/ a fixed scale, KCF w/ three different scales, STC,
  Struck
\begin{itemize}
\item Visual tracker benchmark (VTB)
\item DTB-70: w/ and w/o motion estimation,
\item UAV123 \footnote{A set of images acquired from an UAV is called
  ``UAV123'' and publicly available from
  https://ivul.kaust.edu.sa/Pages/Dataset-UAV123.aspx}
\item VOT
\end{itemize}
\item Conclusion
\end{itemize}

>>>>

\begin{itemize}
\item Introduction: Should talk about, at least, motivation of this
  work, brief review of the literature, and contribution
\item Method: Detail the method w.r.t. a diagram of system
  architecture or pseudo code
\begin{itemize}
\item Kernelized Correlation Filter
\item A variant of KCF: Multiple KCF w/ PF ({\it E}nKCF, ${\it E}nKCF_{+RD}$
\item Re-detection for re-initialization: Modules for reliably
  detecting target-lost, for extensively searching the lost target,
  and for picking up the same target with a help from an appearance
  model or other models.
\begin{itemize}
\item To filter out unlikely box proposals,
\begin{itemize}
\item Use a prior information about box, our outputs, dimensions
  (e.g., a combination of width and height, aspect ratio, etc.)
\item Use the information about the trajectory of the target before we
  lose the target.
\end{itemize}
\item MTH: revisited
\item To make a box tighter, generate our own box proposals based on
  the locations of top $k$ box proposals from object proposal methods,
  e.g., Edge Box.
\end{itemize}
\end{itemize}
\item Experiment: Detail the data, and experimental setup; results and findings
\item Will compare the performance of {\it E}nKCF, Naive{\it E}nKCF,
  ${\it E}nKCF_{+RD}$ with those of the following tracking methods.
\begin{itemize}
\item LCT (Long-term Correlation Tracking),
\item vanilla-KCF w/ a fixed scale,
\item vanilla-KCF w/ three different scales,
\item MEEM (Multiple Experts using Entropy Minimization)
\item SAMF (Scale Adaptive KCF)
\item STC (fast tracking via Spatio-Temporal Context learning),
\item Struck (Structured Output Tracking with Kernels)
\end{itemize}
\begin{itemize}
\item Visual tracker benchmark (VTB)
\item DTB-70: w/ and w/o motion estimation,
\item UAV123 \footnote{A set of images acquired from an UAV is called
  ``UAV123'' and publicly available from
  https://ivul.kaust.edu.sa/Pages/Dataset-UAV123.aspx}
\item VOT
\end{itemize}
\item Conclusion
\end{itemize}
